### 2022-10-25 README.Rmd
readme update

This repository contains the R code and other materials for the paper "Comparing corrosion control treatments for drinking water using a robust Bayesian generalized additive model", currently available as a [preprint](http://doi.org/10.26434/chemrxiv-2022-b3f72-v4). Bespoke functions used to fit the models are available as a separate package, [`bgamcar1`](https://github.com/bentrueman/bgamcar1).

>>>>

This repository contains the R code and other materials for the [paper](https://doi.org/10.1021/acsestengg.2c00194) "Comparing corrosion control treatments for drinking water using a robust Bayesian generalized additive model", also available as a [preprint](https://doi.org/10.26434/chemrxiv-2022-b3f72-v5). Bespoke functions used to fit the models are available as a separate package, [`bgamcar1`](https://github.com/bentrueman/bgamcar1).
